### 2017-10-29 monograph/thesis/chapters/introduction.tex
Created 3 new references and referenced the introduction.tex
second paragraph. References:
Towards Automatic Synthesis of Software Verification Tools
An Annotation Assistant for Interactive Debugging of Programs with Common Synchronization Idioms

    % TODO, put reference for this
    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{naturalCodingConventions}

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for
    discoursing. Nonetheless, in this work is presented the implementation of
    tool called `Object Beautifier', which specifically dedicates on how to
    perform the best layout/display of programming code on the computer screen,
    so that maximize and facilitate the understanding of same. Therefore,
    allowing the programmer to disperse more tempe thinking about its coding
    algorithms problem, other than trying to decipher the information that is
    presented to it on the screen through infinit different code layouts.

@@

    \cite{codePlagiarismDetection}
    \cite{softwarePortfolio}
    \cite{legacyAssets}
    \cite{massMaintenance}
    \cite{prettyPrinting}
    \cite{architectureFormatting}
    \cite{independentFramework}
    \cite{programIndentation}
    \cite{industrialApplication}
    \cite{toolsForProjectManagement}

>>>>

    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{naturalCodingConventions}

    But entering the universe of good practices, there are many things for
    discoursing. Nonetheless, in this work is presented the implementation of
    tool called `Object Beautifier', which specifically dedicates on how to
    perform the best layout/display of programming code on the computer screen,
    so that maximize and facilitate the understanding of same
    \cite{automaticSynthesis}. Therefore, allowing the programmer to disperse
    more tempe thinking about its coding algorithms problem, other than trying
    to decipher the information that is presented to it on the screen through
    infinit different code layouts.

@@

    Application fields for code beautifiers:
    \cite{annotationAssistant}
    \cite{codePlagiarismDetection}
    \cite{softwarePortfolio}
    \cite{legacyAssets}
    \cite{massMaintenance}
    \cite{prettyPrinting}
    \cite{architectureFormatting}
    \cite{independentFramework}
    \cite{programIndentation}
    \cite{industrialApplication}
    \cite{toolsForProjectManagement}

### 2017-10-29 monograph/thesis/postexto/abstracts.tex
Created 3 new references and referenced the introduction.tex
second paragraph. References:
Towards Automatic Synthesis of Software Verification Tools
An Annotation Assistant for Interactive Debugging of Programs with Common Synchronization Idioms

>>>>

    \item \textbf{An annotation assistant for interactive debugging of programs
    with common synchronization idioms}: This paper explores an approach to
    improving the practical usability of static verification tools for debugging
    synchronization idioms. Synchronization idioms such as mutual exclusion and
    readers/writer locks are widely-used to ensure atomicity of critical
    regions. We present an annotation assistant that automatically generates
    program annotations. These annotations express noninterference between
    program statements, ensured by the synchronization idioms, and are used to
    identify atomic code regions. This allows the programmer to debug the use of
    the idioms in the program. We start by formalizing several well-known idioms
    by providing an abstract semantics for each idiom. For programs that use
    these idioms, we require the programmer to provide a few predicates linking
    the idiom with its realization in terms of program variables. From these, we
    automatically generate a proof script that is mechanically checked. These
    scripts include steps such as automatically generating assertions and
    annotating program actions with them, introducing auxiliary variables and
    invariants. We have successfully shown the applicability of this approach to
    several concurrent programs from the literature.
    \cite{annotationAssistant}
